---
title: "Introduction to *document*"
author: "Andreas Dominik Cullmann"
date: 2017-04-28, 10:57:27
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


# Writing Documentation Files to Disk
Suppose you have a script

```{r, comment = ""}
path <- system.file("tests", "files", "minimal.R", package = "document")
cat(readLines(path), sep = "\n")
```
Then
```{r, result = "hide", message = FALSE}
d <- document::document(file_name = path, check_package = FALSE)
```
creates a
Portable Document Format 
[(pdf)](https://en.wikipedia.org/wiki/Portable_Document_Format) file,
an Hypertext Markup Language
[(html)](https://en.wikipedia.org/wiki/HTML) file and a 
[plain text](https://en.wikipedia.org/wiki/Plain_text) file.
The plain text reads
```{r, comment = ""}
cat(readLines(d[["txt_path"]]), sep = "\n")
```

```{r, echo = FALSE, results = "hide", message = FALSE}
d <- document::document(file_name = path, 
                        output_directory = file.path(rprojroot::find_root(rprojroot::is_r_package), 
                                                     "inst", "tests", "files"),
                        check_package = FALSE)
file.remove(unlist(d[c("txt_path", "pdf_path")]))
```

You can view a copy of the html file [here](http://htmlpreview.github.io/?https://github.com/fvafrCU/document/blob/master/inst/tests/files/minimal.html). 
The pdf file resembles a package's documentation pdf file.



# Displaying Temporary Help Files
You can display the help page for one of the documented functions using
```{r, comment = ""}
options(pager = switch(.Platform[["OS.type"]], "unix" = "cat", "console"))
document::man("foo")
```
but I can't figure how to caputure it's output knitring R markdown vignette.
